---
title: "Research Paper Title"
author: "Author Name"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    template: null
    includes:
      in_header: !expr here::here("latex", "preamble.tex")
    toc: true
    toc_depth: 3
    number_sections: true
    fig_caption: true
    keep_tex: true
documentclass: jlreq
classoption: [paper=a4paper,fontsize=11pt]

---

# Introduction

この文書をコピーしてレポート・論文を作成してください。
日本語用に設定しています。上のfontsizeを11ptから12または10などに変えると、フォントサイズも変更できます。


## Math Test
Inline math: $E = mc^2$

Display math:
$$
\int_{-\infty}^{\infty} e^{-x^2} dx = \sqrt{\pi}
$$


## Figures and Tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  fig.align = 'center',
  fig.width = 8,
  fig.height = 6,
  dpi = 300
)
library(ggplot2)
library(here)
```

```{r example-plot, fig.cap="Sample Plot"}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point(alpha = 0.7, size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(
    x = "Weight (1000 lbs)", 
    y = "Miles per gallon",
    title = "Weight vs MPG"
  ) +
  theme_minimal()
```

## Table Example

```{r example-table}
library(knitr)

mtcars_sample <- head(mtcars[, 1:6], 8)
kable(
  mtcars_sample, 
  caption = "Sample of mtcars data",
  digits = 2,
  booktabs = TRUE
)
```

## Path Management

This template uses `here::here()` for absolute paths from project root.

## Notes

Using `template: null` disables R Markdown default template, allowing `documentclass: jlreq` to work properly.
